Ethnicity sensitive author disambiguation using semi-supervised learning

### 2015-08-28 paper/paper.tex
small change

Note that the maximum recalls of blocking strategies using phonetization are
raised also due to the better handling of multiple given names cases described in Section \ref{methods:blocking}.

>>>>

Note that the maximum recalls of blocking strategies using phonetization are
also raised due to the better handling of multiple given names cases, as described in Section \ref{methods:blocking}.
